### 2020-07-23 paper/main.tex
Finding jewels, t1 and t2 wip

\newcommand{\TODO}{\todo[inline]}
\newcommand\Lovasz{Lovász }

@@

\paragraph{Editorial notes}
By solid lines we will mark edges, by dashed lines we will mark nonedges, when significant. Sometimes nonedges will not be marked in order not to clutter the image.
\todo{Where should we put it?}

@@

\begin{wrapfigure}[12]{r}{0.35\textwidth}
	\centering\begin{tikzpicture}[scale=0.7,simplegraph]
	\def\ngon{5}
	\node[regular polygon,regular polygon sides=\ngon,minimum size=3cm, draw=none] (p) {};
	\foreach\x in {1,...,\ngon}{\node[] (p\x) at (p.corner \x){$v_\the\numexpr\intcalcMod{\x+3}{5}+1$};}
	%p1 - v5, p2 - v1 ...
	\draw (p1) to (p2);
	\draw (p2) to (p3);
	\draw (p3) to (p4);
	\draw (p4) to (p5);
	\draw (p1) to (p5);

@@

Recognizing simple structures (Pyramids, Jewels, T1, T2, T3).\\

@@

Optimizations - Bottlenecks in performance (next path, are vectors distinct etc).\\

>>>>

\newcommand{\TODO}{\todo[inline]}
\newcommand\Lovasz{Lovász }
\newcommand\T{\mathcal{T}}

@@

\paragraph{Editorial notes}
\begin{itemize}
	\item By solid lines we will mark edges, by dashed lines we will mark nonedges, when significant. Sometimes nonedges will not be marked in order not to clutter the image.
	\todo{Where should we put it?}
	\item A node is $X$-complete in $G$ iff it is adjacent to all nodes in $X$.
	\item Given a path $P$, by $P^*$ we will denote its inside.
\end{itemize}

@@

\begin{wrapfigure}[7]{r}{0.35\textwidth}
	\centering\begin{tikzpicture}[scale=0.7,simplegraph]
	\def\ngon{5}
	\node[regular polygon,regular polygon sides=\ngon,minimum size=3cm, draw=none] (p) {};
	\foreach\x in {1,...,\ngon}{\node[] (p\x) at (p.corner \x){$v_\the\numexpr\intcalcMod{\x+3}{5}+1$};}
	%p1 - v5, p2 - v1 ...
	\draw (p1) to (p2);
	\draw (p2) to (p3);
	\draw (p3) to (p4);
	\draw (p4) to (p5);
	\draw (p1) to (p5);

@@

Most obvious way to find a jewel would be to enumerate all choices of $v_1, \ldots v_5$, check if a choice is correct and if it is try to find a path $P$ as required. This gives us a time of $O(|V|^7)$. We could speed it up to $O(|V|^6)$ with more careful algorithm, but since whole algorithms takes time $O(|V|^9)$ and our testing showed that time it takes to test for jewels is negligible we used this simple algorithm.

\paragraph{Configurations of type $\T_1$}

A configuration of type $\T_1$ is a hole of length 5. To find it we simply iterate all choices of paths of length of 4, and check if there exists a fifth node to complete the hole. See paragraph \ref{Optimizations} for more implementation details.

\paragraph{Configurations of type $\T_2$} A configuration of type $\T_2$ is a six $(v_1, v_2, v_3, v_4, P, X)$, such that:
\begin{itemize}
	\item $v_1v_2v_3v_4$ is a path in $G$.
	\item $X$ is an anticomponent of the set of all $\{v_1, v_2, v_4\}$-complete nodes.
	\item $P$ is a path in $G\setminus(X \cup \{v_2, v_3\})$ between $v_1$ and $v_4$ and no vertex in $P^*$ is $X$-complete or adjacent to $v_2$ or adjacent to $v_3$.
\end{itemize}

Checking if configuration of type $\T_2$ exists in our graph is straightforward: we enumerate all paths $v_1\ldots v_4$, calculate set of all $\{v_1, v_2, v_4\}$-complete nodes and its anticomponents. Then, for each anticomponent $X$ we check if required path $P$ exists.

@@

\subsubsection{Optimizations}\label{Optimizations}
Bottlenecks in performance (next path, are vectors distinct etc).\\
\TODO{In our graph preprocessing we have a pointer to next edge in order to speed up generating next path.}
\TODO{We used callgrind to get idea of methods crucial for time.}
\TODO{In general enumerating all paths is crucial. As is checking if vector has distinct values.}
\TODO{Jewels -- we iterate all possibly chordal paths and check if they are ok - much faster}
\TODO{$\T_1$ -- we iterate all paths of length 4 and check if there exists a fifth node to complete the hole - much faster than iterating nodes.}
